\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2\baselineskip}

### 2016-09-19 document/ms.tex
clearing up wording in conclusion for comparisons with ulens

\response{%
\citet{Clanton:2016} studied the occurrence rate of long-period giant planets
orbiting M dwarfs by combining results from radial velocity, microlensing, and
direct imaging surveys.
In the period and mass range $10^3-10^4\unit{days}$ and $10-10^4\,M_\oplus$,
they find a mean occurrence rate density of
\begin{eqnarray}
\frac{\dd^2 N}{\dd\ln M\,\dd\ln P} &=& 0.023
\end{eqnarray}
% \begin{eqnarray}
% \frac{\dd^2 N}{\dd\ln M\,\dd\ln P} &\lesssim& 0.013
% \end{eqnarray}
per M dwarf with large uncertainty.}
This result is slightly lower than our estimated rate for a similar range of
masses and periods but around G/K dwarfs.
This difference is consistent with previous results that cooler stars host
fewer long-period giant planets \citep[for example][]{Cumming:2008}.

@@

We measure the empirical detection efficiency function of our search procedure
by injecting simulated transit signals into the target light curves and
measuring the recovery rate.
By combining the measured detection efficiency and the catalog of exoplanet
candidates, we estimate the integrated occurrence rate of exoplanets with
orbital periods in the range $2-25\unit{years}$ and radii in the range
$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K dwarf.
This result is qualitatively consistent with estimates from radial velocity,
microlensing, and direct imaging surveys.

>>>>

\response{%
\citet{Clanton:2016} studied the occurrence rate of long-period giant planets
orbiting M dwarfs by combining results from radial velocity, microlensing, and
direct imaging surveys.
In the period and mass range $10^3-10^4\unit{days}$ and $10-10^4\,M_\oplus$,
they find a mean occurrence rate density of
\begin{eqnarray}
\frac{\dd^2 N}{\dd\ln M\,\dd\ln P} &=& 0.023
\end{eqnarray}
% \begin{eqnarray}
% \frac{\dd^2 N}{\dd\ln M\,\dd\ln P} &\lesssim& 0.013
% \end{eqnarray}
per M dwarf with large uncertainty.}
This result is slightly lower than our estimated rate for a similar range of
masses and periods but around G/K dwarfs.
\response{%
This difference is consistent with previous observational and theoretical
results that cooler stars host fewer long-period giant planets \citep[for
example][]{Laughlin:2004, Cumming:2008, Clanton:2016}.
}

@@

We measure the empirical detection efficiency function of our search procedure
by injecting simulated transit signals into the target light curves and
measuring the recovery rate.
By combining the measured detection efficiency and the catalog of exoplanet
candidates, we estimate the integrated occurrence rate of exoplanets with
orbital periods in the range $2-25\unit{years}$ and radii in the range
$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K dwarf.
\response{%
This result is qualitatively consistent with estimates of the occurrence rate
of long-period giant planets based on data from radial velocity and direct
imaging surveys.
The occurrence rate measured here~--~for Sun-like hosts~--~is higher than
microlensing results for lower mass stars \citep{Clanton:2014, Clanton:2016}
but this discrepancy is consistent with predictions from the core-accretion
model \citep{Laughlin:2004}.
}
